Democracy, Public Support, and Measurement Uncertainty

### 2021-08-14 paper/dcpo_demsupport.Rmd
add dcpo description in Appendix

# Appendix C: The Method of Composition {#moc}

@@

# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)

@@

# Appendix B: DCPO Replication {#dcpo}

@@

We employed the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].

>>>>

# Appendix B: The Method of Composition {#moc}

@@

# Appendix C: Secondary Models from Claassen (2020$a$, 2020$b$)

@@

# Appendix D: DCPO Replication {#dcpo}

@@

We employ the superior DCPO model to the expanded data using the `DCPO` package for R [@Solt2020b].
We use the estimated public support from DCPO model to replicate analyses by following the same steps.
Then, we compare the DCPO results with two types of replication results from Model 5: estimation of original data and without uncertainty and estimation of expanded data and with uncertainty.

The comparison is presented in Appendix B.
Still, even with the superior DCPO model and expanded data, there is no evidence to support that public support can sustain democratic development or public support responds thermostatically to changes in democracy.
